---
output: github_document
---

```{r setup, include = FALSE}
should_eval <- "tibble" %in% installed.packages()

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# forested: Data on Forest Attributes in Washington State

The U.S. Department of Agriculture, Forest Service, Forest Inventory and Analysis (FIA) Program provides all sorts of estimates of forest attributes for uses in research, legislation, and land management. The FIA uses a set of criteria to classify a plot of land as "forested" or "non-forested," and that classification is a central data point in many decision-making contexts. A small subset of plots in Washington State are sampled and assessed "on-the-ground" as forested or non-forested, but the FIA has access to remotely sensed data for all land in the state. **forested is an R data package** containing a data frame, `forested`, from which we can develop a model on the more easily-accessible remotely sensed data to predict whether a plot is forested or non-forested.

## Installation

Install the development version of forested from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("simonpcouch/forested")
```

## Example

```{r, eval = should_eval}
library(tibble)
library(forested)

forested
```
